Approximation as Differentiation

### 2025-06-01 main/higher-order.tex
Initial pass over mu-polynomial functors.
Explicitly define Pos/Neg.
First pass over semantics of well-kinded types.

\input{fig/mu-polynomial}

\begin{definition}[$\mu$-polynomial]
Suppose $\cat{C}$ a category with finite coproducts and finite products. Define $\muPoly$
to be the smallest subcategory of $\Cat$ closed under the rules in \figref{mu-polynomial}.
\end{definition}

\input{fig/syntax}

@@

\input{fig/typing}

>>>>

\input{fig/positivity}
\input{fig/syntax}
\input{fig/typing}

@@

\input{fig/mu-polynomial}
\input{fig/set-semantics}

\begin{definition}[$\mu$-polynomial]
Suppose $\cat{C}$ a category with finite coproducts and finite products. Define $\muPoly_{\cat{C}}$ to be the
smallest subcategory of $\Cat$ generated inductively by the rules in \figref{mu-polynomial}.
\end{definition}

\figref{set-semantics:types} gives the interpretation of a type $\tau$ with a single free type variable as an
endofunctor on $\Set$.
